Single-cell virus sequencing of influenza variants that trigger innate immunity

### 2018-08-29 paper/paper.tex
Finished updating genotype figure with supplements
Added a supplement that shows for how many cells
we obtained complete viral genotypes, and shows
how we tended to get more viral genotypes for
cells that were **not** co-infected, and for
cells with higher viral mRNA expression.

>>>>

\figsupp[Number of cells for which genotype(s) of infecting viruses were completely determined.]
{Cells for which we could determine the full sequences of all genes expressed by the infecting virus(es).
{\bf (A)} We could call the complete genotypes of the infecting virus(es) for the majority of cells infected with just a single viral barcode variant, but only a minority of cells co-infected with both viral barcodes.
{\bf (B)} The cells for which we could call complete viral genotypes tended to have higher expression of viral mRNAs than cells for which we could not call complete genotypes.
This makes sense, as cells with more viral mRNA are more likely to have their viral genes captured in the PacBio sequencing, which is only able to capture a small fraction of the total transcripts identified by the 3'-sequencing of the 10X platform.
The lower calling rate for dual-barcode co-infections relative to single barcode infectionis is probably because these co-infections have more viral genes that must be sequenced (potentially a copy of each viral gene from each viral variant), increasing the chances that one of these genes is missed by the PacBio sequencing. 
An important implication of this plot is that the cells for which we call complete viral genotypes are \emph{not} a random subsampling of all infected cells in the experiment, but are rather enriched for cells that have high levels of viral mRNA and do not have dual-barcode viral infections.
Note also that this plot is limited to the cells that were called as infected (\FIG{experiment}D) and could clearly be classified as IFN- or IFN+ (\FIG{experiment}H).
}
{\includegraphics[width=0.8\textwidth]{figures/single_cell_figures/p_cells_complete.pdf}}
